Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix grammar.

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (partial) list of WebRTC specific protocols drafts and other
related protocol standards for the first three functionality groups
(data transport, data framing and security, and connection
management).

>>>>

The last three functionality groups focus on interactive audio and video
applications and are less relevant to Raft over WebRTC. The WebRTC
section of the bibliography %TODO: reference link
has a (partial) list of WebRTC specific protocol drafts and other
related protocol standards for the first three functionality groups
(data transport, data framing and security, and connection
management).
